---
title: "Activity 8 - Mini-competition"
Author: Durga
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
---
title: "Inventory Report"
output: Inventory.pdf
date: "2023-07-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Loading the libraries and packages as required

- With using Tidymodel package/Library we will achieve the prediction model for this scenario

```{r}
library(dplyr)
library(ggplot2)
#install.packages("tidymodels")
library(tidymodels)
```
#Loading the file and summary of the file

 - Read and create the data to a Dataframe
- Dimensions of the file : 3 Columns, 26,352 rows data
- Item character and Week, Sold numerical data

```{r}
test_file <- read.csv("/Users/saranyat/Downloads/inventory.csv")
test_file

summarise(test_file)
head(test_file)
```

#Subset the data with filtering for items only sold > 0 items

- Filtering data makes it less complex and more efficient

```{r}
fd <- test_file[test_file$sold > 0, ]
fd

```


#Splitting the data into Training and Test data sets for the model based on the Filtered data above

- Training dataset = 80%
- Testing data = 20%

```{r}

# Split the data into training and testing sets manually
set.seed(123)
na.omit(fd)
trainIndex <- sample(nrow(fd), floor(0.8 * nrow(fd)))
trainData <- fd[trainIndex, ]
testData <- fd[-trainIndex, ]

trainData
testData

```

#Train and creating a linear regression model with "Tidymodel"

```{r}
# Fit a linear regression model

lmodel <- lm(sold ~ item_no + week, data = trainData)
lmodel

```
```{r}

library(tidyr)
trainData$item_no <- replace_na(trainData$item_no, "NA")


testData$item_no <- replace_na(trainData$item_no, "NA")


levels(trainData$item_no)

levels(testData$item_no)

testData$item_no <- factor(testData$item_no, levels = levels(trainData$item_no))


class(lmodel)

str(testData)  # This will show the structure of the 'futureData' dataset

future_predictions <- predict(lmodel, newdata = testData)

# ensure that the futureData dataset has the same levels for the categorical variable item_no as the trainData dataset. Here's a step-by-step guide to fix the issue:

summary(future_predictions)
```


```{r}
# Making predictions on the test data

testData$item_no <- factor(testData$item_no, levels = levels(trainData$item_no))
predictions <- predict(lmodel, newdata = testData)

summary(predictions)

```




```{r}

# Evaluate model performance
mse <- mean((predictions - testData$sold)^2)
rmse <- sqrt(mse)
cat("Root Mean Squared Error (RMSE):", rmse, "\n")


```
